### 2017-11-15 Draft2/Appendix.tex
Rework A.7

\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequality})]
	Suppose that $f \FluteLess g$. By definition, $\ExprNToInfty \dfrac{f}{g} < 1$. For any function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.

@@

\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequalityAdd})]
	If $\dfrac{f}{h}$ does not approach $0$ as $n \to \infty$, then it is bounded below by some positive constant $c_1$, and $\ExprNToInfty \dfrac{c_1 h}{f} \leq 1$. From $f \FluteLess g$, it follows that $\ExprNToInfty \dfrac{f}{g} < 1$. Since $g = O(h)$, $\exists c_2 : \ExprNToInfty \dfrac{g}{c_2 h} \leq 1$. Multiplying these limits, I receive
	\begin{align*}
	\left( \ExprNToInfty \frac{c_1 h}{f} \right) \left( \ExprNToInfty \dfrac{f}{g} \right) \left( \ExprNToInfty \dfrac{g}{c_2 h} \right) = \ExprNToInfty \frac{c_1 h}{c_2 h} = \frac{c_1}{c_2}
	\end{align*}
	Since at least one limit is less than $1$ and no limit exceeds $1$, the product, $\dfrac{c_1}{c_2}$, is less than $1$. Now, consider that
	\begin{align*}
	\ExprNToInfty \frac{f + h}{g + h} \leq \ExprNToInfty \frac{c_1 h + h}{c_2 h + h} = \frac{c_1 + 1}{c_2 + 1}
	\end{align*}
	Since $c_1 < c_2$, $c_1 + 1 < c_2 + 1$ so $\dfrac{c_1 + 1}{c_2 + 1} < 1$. Thus, $f + h \FluteLess g + h$.

>>>>

\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequality})]
	Suppose that $f \FluteLess g$. By definition, $\ExprNToInfty \dfrac{f}{g} < 1$. For any positive function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.

@@

\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequalityAdd})]
	Assume that $n$ is arbitrarily large. Since $\dfrac{f}{h}$ has a positive limit, it is bounded below by some positive constant $c_1$. Rearranging, $c_1 h \leq f$. From $f \FluteLess g$, it follows that $f < g$ for sufficiently large $n$. Since $g = O(h)$, $\exists c_2 : g \leq c_2 h$. Combining these inequalities, I receive $c_1 h \leq f < g \leq c_2 h$. From this, it is clear that $c_1 < c_2$.

	Now, consider that
	\begin{align*}
	\ExprNToInfty \frac{f + h}{g + h} \leq \ExprNToInfty \frac{c_1 h + h}{c_2 h + h} = \frac{c_1 + 1}{c_2 + 1}
	\end{align*}
	Since $c_1 < c_2$, $c_1 + 1 < c_2 + 1$ so $\dfrac{c_1 + 1}{c_2 + 1} < 1$. Thus, $f + h \FluteLess g + h$.
